Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.0)} \underline{Drafting Committee: DC90 (\today)}

### 2011-06-13 background_and_systematic.tex
Clarified the background section including some of the collaborations comments. Mostly cleaned up the structure and made a clear ordering of systematic effects.

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined as in Refs.~\cite{Air08,Air09}. Contributions to the uncertainties on the amplitude measurements arise from background in the data from neutral meson production. The procedure is described in detail in Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of the measurements addressed here are given in Table~\ref{table_systematic_contributions_0607} for the amplitudes extracted in a single bin in the H{\sc ermes} kinematic region.

Another contribution to the systematic uncertainty comes from the relative shift of the
missing-mass distributions. There are shifts in the distributions for electron and positron data~\cite{Zei09,Bur10}. The missing-mass
distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for the observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty. The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing effects due to detector resolution and radiative processes, and
finite bin width in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was used for the simulation because it describes the data well and is consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted from these simulated events using the same analysis
procedure used to extract amplitudes from experimental data. In each kinematic
bin, the systematic uncertainty was determined as the difference between the
asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.
The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background corrections, detector effects and missing-mass shift
uncertainties added in quadrature. 
The 1996-2005 sample also has a systematic uncertainty from misalignment of the spectrometer, 
which has been eliminated for the 2006-2007 data sample.
These contributions are summarised in Table
\ref{table_systematic_contributions_0607}.

>>>>

\section{Background Corrections and Systematic Uncertainties}
The extracted asymmetry amplitudes are subject to systematic uncertainties that
result from a combination of background processes, 
shifts in the missing-mass distributions and various detector and binning
effects determined in \red{the same manner as in} Refs.~\cite{Air08,Air09}.

The contribution to the uncertainties on the amplitude measurements
\red{arising} from background in the data from neutral meson
production \red{is predominantly due to the misidentification of
  $\pi^0$ mesons}. The procedure is described in detail in
Refs.~\cite{Air08,Air09} and the contributions to the uncertainties of
the measurements addressed here are given in
Table~\ref{table_systematic_contributions_0607} for the amplitudes
extracted in a single bin in the H{\sc ermes} kinematic
region. \red{Each  measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty included as part of the
  total systematic uncertainty.}

\red{The} contribution to the systematic uncertainties from the relative shift of the
missing-mass distributions \red{arises due to} shifts in the
distributions \red{between} electron and positron data~\cite{Zei09,Bur10}. The
missing-mass distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for \red{an} observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty.

The predominant contribution to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing
effects due to detector resolution and radiative processes, and
\red{the} finite bin width \red{of the} $-t$, $x_{\textrm{B}}$ and $Q^{2}$ \red{projections}. In order to quantify
these effects, events were generated using a Monte Carlo simulation of
the spectrometer that included them. An event
generator based on the GPD model described in Ref.~\cite{Guz06} was
used for the simulation because it describes the data well and is
consistent with Ref.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
calculated from the same GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

The total systematic uncertainty for the 2006-2007 data sample was
determined for each kinematic bin from the uncertainty contributions of the
background correction, missing-mass shift, and detector effect
uncertainties added in quadrature.  The 1996-2005 sample also has a
systematic uncertainty from misalignment of the
spectrometer~\cite{Air09}, which has been eliminated for the 2006-2007 data sample \red{due to improved
  surveying measurements of the spectrometer~\cite{Bur10}. The contribution from
each uncertainty to each amplitude extracted in a single kinematic bin
from the 2006-07 data  is summarised in Table
\ref{table_systematic_contributions_0607}.}

The beam polarisation measurement has a total uncertainty of 2.8\% and 3.4\% for the 1996-2005 and 2006-2007 data taking periods respectively,
which is present in the beam-helicity amplitudes and is quoted as an
independent scale uncertainty. \red{The systematic uncertainty quoted for each
  amplitude measurement therefore does not include any uncertainty due to the
  measurement of the beam polarisation.}
